%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart
    
    \resumeProjectHeading
        {\textbf{Brain–Computer Interface Game for a Locked-In Pediatric Patient (Ongoing) \href{https://github.com/fyp21-bci/.github}{\faExternalLink*}} $|$ \emph{Python, OpenBCI, Unity}}{}
    \resumeItemListStart
        \resumeItem{Developing a non-invasive EEG-based BCI system to allow a 6-year-old locked-in patient to control a simple game using brain signals.}
        \resumeItem{Building lightweight ML classifiers optimized for real-time inference on embedded hardware, targeting low-latency and high reliability.}
        \resumeItem{Designing an improved custom dry-electrode headset in SolidWorks, addressing fit and contact, prototyping and mechanical testing are in progress.}
        \resumeItem{Developing a Unity-based game interface with patient-specific thresholds to support gradual training and engagement.}
        \resumeItem{Secured a grant worth of 1 Million LKR to purchase OpenBCI Products by demonstrating the project to sponsors.}
        \quad
    \resumeItemListEnd
    
    \resumeProjectHeading
        {\textbf{Human Height Measuring Under Low Ultrasound Reflection due to Dense Scalp Hair \href{https://github.com/chathuracns/Human-Height-Measuring-Under-Low-Ultrasound-Reflection-due-to-Dense-Scalp-Hair}{\faExternalLink*}} $|$ \emph{tinyML, SolidWorks, Altium}}{}
    \resumeItemListStart
        \resumeItem{Preprocessed a dataset of ultrasound reflections, accounting for acoustic transmission losses and field alterations caused by scalp hair, and conducted manual analysis to identify patterns due to the limited size of the dataset.}
        \resumeItem{Implemented a K-means clustering algorithm to classify data clusters corresponding to reflections from hair.}
        \resumeItem{Enhanced detection accuracy to 3 cm level, even under conditions of extremely low ultrasound reflection.}
        \resumeItem{Selected for a grant from the World Bank funded AHEAD (Accelerating Higher education Expansion and Development) program.}
        \quad
    \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Dynamic Body-Weight Support System Using a Motorized Unloader for Rehabilitation \href{https://github.com/chathuracns/Zero-G-Dynamic-Body-Weight-Support-System-Using-a-Motorized-Unloader}{\faExternalLink*}} $|$ \emph{Matlab, AVR}}{}
    \resumeItemListStart
        \resumeItem{Analyzed load cell and position encoder signals to detect the rate of tension generated on the supporting rope.}
        \resumeItem{Implemented and simulated a digital PID controller in MATLAB to validate the control strategy.}
        \resumeItem{Deployed a digital PID Controller using WinAVR on an ATmega328P Micro-controller.} 
        \quad
    \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{ECG Signal Extracting and Monitoring Using Analog Electronics and Wet Electrodes \href{https://github.com/chathuracns/ECG-Signal-Extracting-and-Monitoring-Using-Analog-Electronics-and-wet-electrodes}{\faExternalLink*}} $|$ \emph{LT-Spice, Multisim, Altium}}{}
    \resumeItemListStart
        \resumeItem{Analog Circuit Design: Right Leg Drive, Amplifiers, Filters (high pass, low pass, notch, Butter-worth, Bessel Thomson).}
        \resumeItem{Op-Amp selection (TL072CP) evaluated the parameters like slew rate, offset voltage, noise characteristics.}
        \resumeItem{Use of Fast Fourier Transform techniques to evaluate effectiveness of the filters.}
    \resumeItemListEnd
    
    \resumeProjectHeading
        {\textbf{Redesign Human Height Measuring as a Device Focusing on US FDA Regulation \href{https://github.com/chathuracns/Re-design-Human-Height-Measuring-as-a-Device-Focusing-on-US-FDA-Regulation}{\faExternalLink*}} $|$ \emph{FDA databases}}{}
    \resumeItemListStart
        \resumeItem{Classified the device into risk class (I, II, III).}
        \resumeItem{Re-Design the product enclosure for 510(k) Pre-market Notification.}
        \resumeItem{Familiarity with FDA databases.}
        \quad
    \resumeItemListEnd

    \begin{comment}
    \resumeProjectHeading
        {\textbf{EcoWatt Field Gateway for Inverter Monitoring \href{https://docs.google.com/document/d/18SiAOJTwsafdJqaXoMqMdF3TOuyXTFAseOsylDLD3i8/edit}{\faExternalLink*}} $|$ \emph{ESP8266/NodeMCU,Modbus Protocol, FOTA}}{} 
    \resumeItemListStart
        \resumeItem{Design and implement a field gateway (EcoWatt Device) to poll a simulated solar inverter (Inverter SIM) via a cloud API.}
        \resumeItem{Integrate FOTA (Firmware Over-The-Air) functionality, supporting secure, chunked downloads, SHA-256 integrity verification, and rollback safety for firmware updates.}
        \resumeItem{Implement a lightweight security layer (HMAC-SHA256 for integrity and anti-replay protection) and power optimization techniques (DVFS/sleep) suitable for MCU constraints.}
    \resumeItemListEnd 
    \end{comment}

    \begin{comment}
    \resumeProjectHeading
        {\textbf{Implementing a Complete Embedded System for a Medibox} $|$ \emph{Node-RED, MQTT protocol, NTP, ESP32}}{}
    \resumeItemListStart
        \resumeItem{ESP32 micro-controller programming, Designing Node-RED dashboard for remote monitoring}
        \resumeItem{MQTT protocol for IoT communication}
    \resumeItemListEnd
    \end{comment}

    \begin{comment}
    \resumeProjectHeading
        {\textbf{Smart Fitness Band with Custom Tension Sensing and Gamified Endurance Tracking} $|$ \emph{ESP32, Analog Front-End (AFE), Embedded Systems, Real-Time Signal Processing}}{}
    \resumeItemListStart
        \resumeItem{Developed a custom analog front-end circuit to measure fitness band tension accurately using microcontroller ADC input}
        \resumeItem{Implemented an ESP32-based system to track tension magnitude and time-under-tension in real time}
        \resumeItem{Built a gamified software experience where tension + endurance time act as gameplay variables for interactive training feedback}
    \resumeItemListEnd
    \end{comment}

\resumeSubHeadingListEnd