%-------------------------
% Cover Letter in Latex
% Author : Audric Serador
% Updated for: Research Assistant (HCI) - Mental Health Focus
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{multicol}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{graphicx}
\input{glyphtounicode}
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}

\setlength{\tabcolsep}{0in}
\pdfgentounicode=1

\begin{document}

%----------HEADING----------%
\noindent
\textbf{\Huge \scshape Chathura Nirmal Weerasinghe} \\[0.5em]
\noindent
\textbf{\href{https://www.chathuranirmal.com}{www.chathuranirmal.com}} \quad \small \faPhone \ +94-770636509 \quad 
\href{mailto:chathuranirmalweerasinghe@gmail.com}{\small \faEnvelope \ chathuranirmalweerasinghe@gmail.com}

\vspace{0.1cm}
\noindent\rule{\textwidth}{1pt}
\vspace{0.8cm}

% --- RECEIVER ---
\noindent\textbf{Hiring Committee},\\
Division of Industrial Design, \\
College of Design and Engineering, \\
Kent Ridge Campus. \\
\vspace{0.8cm}

% --- SUBJECT LINE ---
\begin{center}
    \textbf{Application for Research Assistant (Human-Computer Interaction) – Job ID: 31295}
\end{center}
\vspace{0.5cm}

\noindent Dear Hiring Committee,
\vspace{0.2cm}

\begin{justify}
I am writing to express my interest in the Research Assistant position within the Division of Industrial Design. I am currently a final-year undergraduate in Biomedical Engineering at the University of Moratuwa, Sri Lanka completing my final semester with a CGPA of 3.7/4.0. I expect to graduate in June 2026, and I am eager to apply my technical prototyping skills and personal insights to your project examining youth mental health and everyday technology use.

\vspace{0.3cm} 
\textbf{Lived Experience and Empathy:} Beyond my academic background, I bring a unique perspective to this research as I have personally navigated an anxiety disorder. This lived experience provides me with a firsthand understanding of how mental health conditions can impact a young person's life and their relationship with digital tools. I believe this empathy is vital for conducting sensitive semi structured interviews and facilitating co design workshops where youth participants feel truly understood and safe to share their reflections.

\vspace{0.3cm} 
\textbf{Research and Qualitative Experience:} During my internship at the Department of Human Centered Computing at Monash University, I executed full cycle research workflows. This included contributing to a systematic review on AR cycling attention through full-text review and data extraction, as well as participating in scholarly discussions and peer feedback sessions. These experiences have prepared me to lead qualitative activities, manage study logistics, and contribute to academic outputs.


\vspace{0.3cm} 
\textbf{Academic and Collaborative Foundation:} My coursework in Psychology and Meditation, combined with my role as Assistant Secretary for the IEEE EMBS Student Branch, has equipped me with a strong sociotechnical lens. I have led multidisciplinary teams for World Bank-funded projects and secured significant grants (1 Million LKR) by effectively communicating complex research goals to stakeholders.

\vspace{0.3cm} 
I am confident that my blend of technical expertise in HCI, research experience, and personal understanding of mental health makes me an excellent candidate to support your team. Thank you for your time and consideration.

\end{justify}
\vspace{0.5cm}

\begin{flushleft}
    Sincerely, \\
    \vspace{0.2cm}
    \textbf{Chathura Nirmal Weerasinghe}\\
    Biomedical Engineering Undergraduate\\
    University of Moratuwa\\
    December 23, 2025
\end{flushleft}

\end{document}