%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
    {Research Experience @ Exertion Games Lab
 \href{https://exertiongameslab.org/people}{\faExternalLink*}}{Jan 2025 -- July 2025}
    {Monash University, Clayton Campus, Australia. }{}
    
    \resumeItemListStart
        \resumeItem{Designed "VibroBits," a wearable system for visualizing center-of-pressure via vibrotactile feedback for sports training,\href{https://doi.org/10.1145/3749385.3749418}{\underline{ Demonstrated at SportsHCI '25.}}}

\resumeItem{Developed a gaze aversion detection system integrating Tobii Eye-Trackers, Raspberry Pi, and ESP32 modules to control arm-worn haptic and exoskeleton feedback for \href{https://www.nathalieoverdevest.com/understanding-embodied-remembering}{\underline{"Embodied Remembering" research}}.}

\resumeItem{Prototyped wireless, controllable fragrance diffusers diffusers and wearable thermal neck pads to deliver sensory stimuli for a \href{https://exertiongameslab.org/projects/lucientry-a-lucid-dream-induction-system}{\underline{ lucid dream induction study.}}}

\resumeItem{Designed AR navigation and safety alerts using HoloLens 2 and X-Real glasses to analyse cyclist attention.}

\resumeItem{Contributed to a systematic review on AR cycling attention by assisting with full-text review, data extraction, and manuscript composition.}

\resumeItem{Executed full-cycle research workflows, including gap analysis, literature review, study framework development, and collaborative manuscript revision.}

\resumeItem{Contributed to the lab and its culture by participating in scholarly discussions, research exchanges, and peer feedback sessions.}
             
    \resumeItemListEnd
    

    \resumeSubheading
    {Product Development Experience @ "MeasureUP" 
 \href{https://github.com/chathuracns}{\faExternalLink*}}{Aug 2023 -- Present}
    {World Bank funded AHEAD Project to Develop a Portable BMI Measuring Device for Clinical Settings.}{}
    
    \resumeItemListStart
        \resumeItem{Led a multidisciplinary team on the World Bank-funded Product development project worth 0.5 million LKR }
        \resumeItem{Achieved the budget constraint of 5,000 LKR per unit by using cost-effective sensors and improving its ability for height detection with 3 cm precision by implementing K-means clustering-based machine learning framework}
        \resumeItem{Involved in the complete product design process, ensuring the 3D design met FDA requirements.}       
        \resumeItem{Maintained  legal, financial, and design documentation. Exhibited excellent communication skills in pitching sessions, securing grant approval.}
    \resumeItemListEnd
    
     \href{https://github.com/chathuracns}{\underline{For more details}} \quad

\resumeSubHeadingListEnd